\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{fontawesome}
\setlength{\parindent}{0pt}

% Modern two-column resume structure
%--------------------
%    HEADER
%--------------------
\begin{document}

% HEADER
\begin{center}
    {\LARGE \textbf{Alok Bhateshwar}} \\[2pt]
    Data Scientist \& Web Developer \\[2pt]
    \href{mailto:alokbhateshwar@gmail.com}{\textcolor{blue}{alokbhateshwar@gmail.com}} \quad
    \href{https://github.com/alokbhateshwar}{\textcolor{blue}{\faGithub\ GitHub}} \quad
    \href{https://www.linkedin.com/in/alok-bhateshwar-043202346}{\textcolor{blue}{\faLinkedin\ LinkedIn}}
\end{center}

%--------------------
%    SUMMARY
%--------------------
\section*{Summary}
Computer Science student passionate about Data Science and Web Development. Experienced in building intelligent data-driven solutions and modern web applications. Skilled in Python, Machine Learning, and modern web technologies. Eager to learn and contribute to impactful projects.

%--------------------
%    SKILLS
%--------------------
\section*{Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Programming:} Python, JavaScript, HTML, CSS
    \item \textbf{ML/Data:} Pandas, Scikit-learn, TensorFlow, Keras, NumPy
    \item \textbf{Web:} React, Node.js, Redux, MongoDB
    \item \textbf{Tools:} Git, Jupyter Notebook, YFinance, Matplotlib, Seaborn
\end{itemize}

%--------------------
%    EDUCATION
%--------------------
\section*{Education}
\textbf{Bikaner Technical University} \hfill 2023--2027 \\
B.Tech, Computer Science and Engineering \hfill CGPA: 8.5+ (Current, 3rd Year)

\textbf{SRK Jobner} \hfill 2022--2023 \\
Senior Secondary, Science \hfill Percentage: 83.6\%

%--------------------
%    PROJECTS
%--------------------
\section*{Projects}
\begin{itemize}[leftmargin=*]
    % AI Movie Suggester (paragraph style)
    \item \textbf{AI Movie Suggester} (\href{https://github.com/alokbhateshwar/ai-movie-suggester}{\textcolor{blue}{GitHub}} $\vert$ \href{https://ai-movie-suggester.streamlit.app/}{\textcolor{blue}{Live Demo}}) \\
    \textit{Streamlit, Python, Pandas, TMDB API} \\
    Developed a content-based movie recommender system with a modern UI. Integrated TMDB metadata and a precomputed similarity matrix for instant recommendations, and deployed a live demo for public use.
    % House Price Prediction Model (paragraph style)
    \item \textbf{House Price Prediction Model} (\href{https://github.com/alokbhateshwar/house-price-prediction}{\textcolor{blue}{GitHub}}) \\
    \textit{Python, Scikit-learn, Pandas, Random Forest} \\
    Developed a regression model to predict house prices with high accuracy. The project involved extensive data cleaning, feature engineering, and visualization to ensure robust and interpretable results, leveraging Python, Scikit-learn, Pandas, and Random Forest algorithms.
    % Myntra Clone (paragraph style)
    \item \textbf{Myntra Clone} (\href{https://github.com/alokbhateshwar/myntra-clone}{\textcolor{blue}{GitHub}}) \\
    \textit{React, Node.js, MongoDB, Redux} \\
    Built a full-stack e-commerce platform with authentication and payment integration. Implemented product recommendations and responsive design for a seamless user experience.
    % Personal Portfolio Website (paragraph style)
    \item \textbf{Personal Portfolio Website} (\href{https://github.com/alokbhateshwar/portfolio}{\textcolor{blue}{GitHub}}) \\
    \textit{HTML5, CSS3, JavaScript} \\
    Designed and developed a modern, responsive portfolio website. Integrated smooth animations and interactive elements for enhanced user experience.
    % Additional Projects (paragraph one-liners)
    \item \textbf{CGPA to Package Prediction Model} (\href{https://github.com/alokbhateshwar/cgpa-to-package}{\textcolor{blue}{GitHub}}): Linear Regression for placement package prediction using academic data.
    \item \textbf{Social Ads Logistic Regression Model} (\href{https://github.com/alokbhateshwar/social-ads-logistic}{\textcolor{blue}{GitHub}}): Purchase prediction from social ads using logistic regression.
    \item \textbf{Face Recognition System} (\href{https://github.com/alokbhateshwar/face-recognition}{\textcolor{blue}{GitHub}}): Deep learning for secure authentication and attendance.
    \item \textbf{Customer Churn Prediction} (\href{https://github.com/alokbhateshwar/customer-churn}{\textcolor{blue}{GitHub}}): Machine learning model for customer churn analysis.
    \item \textbf{Stock Price Prediction} (\href{https://github.com/alokbhateshwar/stock-price-prediction}{\textcolor{blue}{GitHub}}): LSTM-based time series forecasting for stock prices.
    \item \textbf{Netflix Data Cleaning} (\href{https://github.com/alokbhateshwar/netflix-data-cleaning}{\textcolor{blue}{GitHub}}): Data analysis and visualization on Netflix content dataset.
    \item \textbf{Pima Indians Dataset Analysis} (\href{https://github.com/alokbhateshwar/pima-indians-analysis}{\textcolor{blue}{GitHub}}): Exploratory data analysis and cleaning on the Pima Indians Diabetes Dataset.
    \item \textbf{Employee Data Analysis} (\href{https://github.com/alokbhateshwar/employee-data-analysis}{\textcolor{blue}{GitHub}}): Analysis of workforce trends and retention using employee data.
    \item \textbf{Medical Charges Analysis} (\href{https://github.com/alokbhateshwar/medical-charges-analysis}{\textcolor{blue}{GitHub}}): Exploratory data analysis of insurance charges based on demographic and health factors.
    \item \textbf{Hotel Booking Analysis} (\href{https://github.com/alokbhateshwar/hotel-booking-analysis}{\textcolor{blue}{GitHub}}): Analysis of hotel booking patterns and trends using Python.
\end{itemize}

%--------------------
%    EXPERIENCE
%--------------------
\section*{Experience}
\textbf{Data Analyst \& Data Scientist Intern} \hfill IT EXPERT, Jaipur \\
\begin{itemize}[leftmargin=*]
    \item Contributed to real-world data analysis projects, gaining hands-on experience in Python, Pandas, and teamwork in a professional environment.
\end{itemize}

\end{document} 